Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-10 Paper/paper.tex
Fixed an issue with the abstract showing up twice

\begin{document}
\maketitle
\begin{abstract}{.Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.\Ben[inline]{This is not true, there are many studies of the evolution of the AS Internet. We should be more specificy about what this statement means, ie with respect to national boundaries}.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

@@

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.}
\end{abstract}

@@

The AS-layer is the highest level of organization of the Internet, with each individual AS consisting of a separately administered network, which could represent a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes. \Steph[inline]{need citations}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each BGP node.  These tables express local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

Because BGP is a distributed protocol, with all connectivity
information stored in the local routing tables, it is challenging to
infer the exact AS topology at any point in time.  There are several
strategies for inferring the AS graph from local information, and no method is perfect.  
BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.\Steph[inline]{Kirts: Please explain BGPStream and what the problem with it is.}
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.

>>>>

\begin{document}
\maketitle

\begin{abstract}Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.\Ben[inline]{This is not true, there are many studies of the evolution of the AS Internet. We should be more specificy about what this statement means, ie with respect to national boundaries}.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

@@

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.
\end{abstract}

@@

The AS-layer is the highest level of organization of the Internet, with each individual AS consisting of a separately administered network, which could represent a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes \cite{bgp}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each BGP node.  These tables express local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

Because BGP is a distributed protocol, with all connectivity
information stored in the local routing tables, it is challenging to
infer the exact AS topology at any point in time.  There are several
strategies for inferring the AS graph from local information, and no method is perfect.  
BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}. BGP dumps and routing table updates
suffer from the fact that BGP paths stored in routing tables reflect only the current knowledge of
a single AS about the routes available. Thus one would need to use many sources to get an accurate picture of
these routes. This approach is not easily scalable for global studies, particularly those looking at multiple time periods.
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.
